---
title: "nleqslv"
output: 
  md_document:
    variant: markdown_github
  
---

<div>
  <table>
    <tr>
      <td>
        <img align="left" width="200" height="200" src="logo.svg"/>
      </td>
    </tr>
  </table>
</div>

```{r setup, include=FALSE}
require(knitr)
```

```{r badges, echo=FALSE, results="asis"}
cat(paste0("|<sub>", 
           paste0(
             c("Actions", "Code Coverage", "Website", "CRAN Downloads", "CRAN"), 
             collapse="</sub>|<sub>"), 
           "</sub>|\n"))
cat(paste0("|", paste0(rep(":---:", 6), collapse="|"), "|\n"))
cat(paste0("|", 
           paste0(c("[![R-CMD-check](https://github.com/bertcarnell/nleqslv/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bertcarnell/nleqslv/actions/workflows/R-CMD-check.yaml)",
                    "[![Codecov test coverage](https://codecov.io/gh/bertcarnell/nleqslv/graph/badge.svg)](https://app.codecov.io/gh/bertcarnell/nleqslv)",
                   "[![](https://img.shields.io/badge/pkgdown-nleqslv-blue.svg)](https://bertcarnell.github.io/nleqslv/)",
                  "[![](https://cranlogs.r-pkg.org/badges/nleqslv)](https://cran.r-project.org/package=nleqslv)",
                  "[![CRAN status](https://www.r-pkg.org/badges/version/nleqslv)](https://cran.r-project.org/package=nleqslv)"), 
                  collapse="|"), 
           "|"))
```

# nleqslv

Solve a system of nonlinear equations using a Broyden or a Newton method with a 
choice of global strategies such as line search and trust region.  There are 
options for using a numerical or user supplied Jacobian,
for specifying a banded numerical Jacobian and for allowing
a singular or ill-conditioned Jacobian.

Original Author:  Berend Hasselman

## Installation

You can install the released version of `nleqslv` from [CRAN](https://CRAN.R-project.org) with:

```{r install1, echo=TRUE, eval=FALSE}
install.packages("nleqslv")
```

You can also install the development version of `lhs` from github with:

```{r install2, echo=TRUE, eval=FALSE}
if (!require(devtools)) install.packages("devtools")
devtools::install_github("bertcarnell/nleqslv")
```

## Quick Start

Start with a function to find solutions for:  High-degree polynomial system from 
Kearfott (1987).

```{r random, echo=TRUE}
require(nleqslv)

hdp <- function(x) {
  stopifnot(length(x) == 3)
  f <- numeric(3)
  f[1] <- 5 * x[1]^9 - 6 * x[1]^5 * x[2]^2 + x[1] * x[2]^4 + 2 * x[1] * x[3]
  f[2] <- -2 * x[1]^6 * x[2] + 2 * x[1]^2 * x[2]^3 + 2 * x[2] * x[3]
  f[3] <- x[1]^2 + x[2]^2 - 0.265625
  f
}

sln <- nleqslv(c(0.2, 0.3, 0.7), hdp, control=list(trace=1))
sln$x
```

Evaluate solutions from the same starting location using multiple methods and
global strategies.

```{r}
testnslv(c(0.2, 0.3, 0.7), hdp)
```

Search for multiple solutions from a variety of starting locations.

```{r}
set.seed(1245323)

N <- 40
xstart <- matrix(runif(3*N, min = -1, max = 1), nrow = N, ncol = 3)
ans <- searchZeros(xstart, hdp, method = "Broyden", global = "dbldog")
ans$x
```
